---
title: "IgG Transplacental"
author: "Usman"
date: "2023-10-20"
output:
  html_document: 
    toc: yes
    number_sections: yes
    theme: journal
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown of my paper on IgG transplacental transfer from mother to her foetus 

## **Introduction**

## **Abstract**

### **Introduction**

Immunoglobulin G (IgG) forms the backbone of the circulating adaptive immune system. Efficient transplacental transfer of maternal adaptive immunity to neonates is crucial for early-life protection against infectious diseases, emphasizing the significance of understanding IgG subclass concentrations and transfer efficiency.

### **Methods**: 

Paired blood samples from 41 mother-infant pairs were collected to evaluate total and subclass IgG levels. Maternal demographic and clinical information was also obtained.

### **Results**: 

Maternal and cord blood showed similar IgG subclass profiles, with a notable gradient of transfer efficiency for IgG subclasses, particularly IgG2 and IgG3, and negative associations between maternal IgG concentrations and transfer ratios.

### **Conclusions**: 

Our findings suggest reduced transplacental transfer of maternal IgG antibodies, emphasizing the role of IgG2 concentration in maternal BMI association and the potential relationship of increased IgG3 levels with antigen-specific response. These results offer valuable insights into the population-specific dynamics of transplacental IgG transfer and warrant further biochemical and physiological investigations.



```{r cars}
library(readxl)
Gestation <- read_excel("~/M.Sc. RAW DATA.xlsx", 
                        sheet = "Sheet1")
Gestation

```

## Including Plots

You can also embed plots, for example:
```{r,echo = FALSE}
library(tidyverse)
```


```{r pressure}

Maternal<-Gestation[-42,]%>%select(c(51:55))%>%
  rename(IgG1="M-IgG1",IgG2="M-IgG2",IgG3="M-IgG3",IgG4="M-IgG4",Total="M-Total")%>%
  pivot_longer(cols = c(IgG1,IgG2,IgG3,IgG4,Total),names_to = "Maternal",values_to = "m_IgG")
          
Cord<-Gestation[-42,]%>%select(c(56:60))%>%
  rename(IgG1="C-IgG1",IgG2="C-IgG2",IgG3="C-IgG3",IgG4="C-IgG4",Total="C-Total")%>%
  pivot_longer(cols = c(IgG1,IgG2,IgG3,IgG4,Total),names_to = "Cord",values_to = "c_IgG")

Maternal$group<- "Maternal"
Cord$group<-"Cord"
fetal<-rename(Cord,Maternal=Cord,m_IgG="c_IgG")

maternalfetal<-rbind(Maternal,fetal)
maternalfetal
```

Note that the `warning = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
```{r, warning=FALSE}
ggplot(data=filter(maternalfetal,Maternal !="Total"),aes(x=group,y=m_IgG*1000))+
  geom_violin(trim = FALSE,col="blue",size=1.5)+
  facet_wrap(~Maternal,nrow=1)+
  stat_summary(fun.y = median, fun.ymin = median, fun.ymax = median,
               geom = "crossbar", width = 0.5)+
  theme_minimal()+scale_x_discrete(limits=c("Maternal","Cord"))+
  theme(strip.text=element_text(size = 13.7,face = "bold"))+
  theme(axis.title.y=element_text(colour="darkblue",size=12,face = "bold"),
        axis.line = element_line(colour="black"),
        axis.text.x = element_text(size = 10),
        axis.ticks = element_line(size = 1))+
  labs(x=element_blank(),y="IgG concentrations μg/ml")+
  theme(axis.text=element_text(size = 6,face = "bold"))+
  ylim(-2500,12500)
```

Transplacental transfer ration

```{r}
library(ggpubr)
ggpaired(
  maternalfetal,x="group",y="log10(m_IgG*1000)", line.size = 0.8,
  line.color = "gray",point.size=2,width=0.8,color = "blue")+
  facet_wrap(~Maternal,nrow = 1,scales = "free")+
  scale_color_manual(name="",values = c("blue","black"))+
  theme_minimal()+stat_compare_means(paired = TRUE)+
  labs(x="",y="IgG concentrations (µ/mg) Log10",front="bold")+
  theme(legend.position = "none",axis.title = element_text(face ="bold",
  color = "darkblue",size = 17),axis.text.x = element_text(face = "bold",
  size = 13))+scale_x_discrete(label = c("Maternal"="Maternal","Cord"="Cord"))

```


Transplacental transfer ratio


```{r, warning=FALSE}
maternalfetaltrans<-cbind(Maternal,Cord)%>%
  select(Maternal,m_IgG,Cord,c_IgG)%>%
  mutate(m_IgG=m_IgG*1000,c_IgG=c_IgG*1000)%>%
  mutate(ratio=log(m_IgG/c_IgG))%>%mutate(log2trans=log2(ratio))%>%
  ggplot(aes(Maternal,log2trans))+
  geom_dotplot(binaxis = "y", binwidth = 0.3, stackdir = "center",
               fill="darkblue")+stat_summary(fun.y = median, fun.ymin = median,
              fun.ymax = median,geom = "crossbar", width = 0.5)+theme_minimal()+
  geom_hline(yintercept = 0,lty="dashed",size=1,color="blue")+
  theme(axis.title.y=element_text(colour="darkblue",size=10,face = "bold"),
        axis.line = element_line(colour="black",size = 1),axis.ticks = element_line(size = 1),
        axis.text.x = element_text(angle = 90,face="bold",vjust = 0.02))+xlab("")+
        ylab("Maternal-Fetal Transfer Ratio")
maternalfetaltrans
```


```{r, warning=FALSE}

maternalfetaltrans_gest<-maternalfetaltrans<-cbind(Maternal,Cord)%>%
  select(Maternal,m_IgG,Cord,c_IgG)%>%
  mutate(m_IgG=m_IgG*1000,c_IgG=c_IgG*1000)%>%
  mutate(ratio=log(m_IgG/c_IgG))%>%mutate(log2trans=log2(ratio))
maternalfetaltrans_gest
```



```{r, warning=FALSE}
library(rstatix)
#Maternal fetal transfer ratio relative to WHO categorized gestational age

gestAge<-Gestation[-42,]%>%select(c(51:55,73))%>%
  rename(IgG1="M-IgG1",IgG2="M-IgG2",IgG3="M-IgG3",IgG4="M-IgG4",
         Total="M-Total")%>%pivot_longer(cols = c(IgG1,IgG2,IgG3,IgG4,Total),
          names_to = "Maternal",values_to = "m_IgG")
gestAge
maternalfetaltrans_gest$GestAge<-gestAge$GestAe
maternalfetaltrans_gest

# using the function "labels+" in factor function
a<-expression(bold(""<="36w"))
b<-expression(bold(37^"0/7"*"w-"*38^"0/7"*w))
c<-expression(bold(39^"0/7"*"w-"*40^"0/7"*"w"))
d<-expression(bold(41^"0/7"*"w-"*41^"0/7"*"w"))
e<-expression(bold("">"42w"))

#pairwise comparison using "library(rstatix)"
pwc <- maternalfetaltrans_gest %>%
  group_by(GestAge)%>%
  dunn_test(ratio~Maternal,p.adjust.method = "none")
pwc <- pwc %>% add_xy_position(x = "Maternal")
pwc


mf_ratio_gestage<-maternalfetaltrans_gest%>%
  mutate(GestAge=recode(GestAge,"<42"=">42"))%>%
  ggplot(aes(Maternal,log2trans))+geom_dotplot(binaxis = "y", binwidth = 0.15,
  stackdir = "center",fill="darkblue")+facet_wrap(~factor(GestAge,
  levels=c("<36","37-38","39-40","41-41",">42"),labels=c(a,b,c,d,e)),
  labeller = label_parsed,nrow = 1)+stat_summary(fun.y = median,
  fun.ymin = median, fun.ymax = median,geom = "crossbar", width = 0.5)+
  theme_minimal()+geom_hline(yintercept = 0,lty="dashed",size=1,color="blue")+
  theme(axis.title.y=element_text("Maternal-Fetal Transfer Ratio",colour="darkblue",
  size=10,face = "bold"),axis.line = element_line(colour="black",size = 1),
  axis.ticks = element_line(size = 1),axis.text.x = element_text(angle = 90,
  face="bold",vjust = 0.02))+stat_pvalue_manual(pwc, tip.length = 0.02, 
  hide.ns = TRUE,bracket.size = 1,size=7,label = "p.adj.signif",color="darkblue" )+
  labs(x=element_blank(),y="Maternal to Fetal transfer ratio (Log10 μg/ml)")
mf_ratio_gestage
```


```{r}
pwc1 <- maternalfetaltrans_gest %>%
  group_by(Maternal)%>%
  dunn_test(ratio~GestAge,p.adjust.method = "none")
pwc1 <- pwc1 %>% add_xy_position(x = "GestAge")
pwc1
mf_ratio_IgG<-maternalfetaltrans_gest%>%
  mutate(GestAge=recode(GestAge,"<42"=">42"))%>%
  ggplot(aes(factor(GestAge,levels=c("<36","37-38","39-40","41-41",">42"),
  labels=c(a,b,c,d,e)),log2trans),labeller=label_parsed)+
  geom_dotplot(binaxis = "y", binwidth = 0.2, stackdir = "center",fill="darkblue")+
  facet_wrap(~Maternal,nrow = 1,labeller=label_parsed)+stat_summary(fun.y = median, 
  fun.ymin = median, fun.ymax = median,geom = "crossbar", width = 0.5)+
  theme_minimal()+geom_hline(yintercept = 0,lty="dashed",size=1,color="blue")+
  theme(axis.title.y=element_text(colour="darkblue",size=10,face = "bold"),
  axis.line = element_line(colour="black",size = 1),
  axis.ticks = element_line(size = 1),axis.text.x = element_text(angle = 90,
  face="bold"))+scale_x_discrete(labels=c(a,b,c,d,e))+stat_pvalue_manual(pwc1,
  tip.length = 0.02, hide.ns = TRUE,bracket.size = 1,size=7,
  label = "p.adj.signif",color="darkblue" )+labs(x=element_blank(),
  y="Maternal to Fetal transfer ratio (Log10 μg/ml)")
mf_ratio_IgG
```



```{r, warning=FALSE}
A<-mf_ratio_gestage+rremove("ylab")
B<-mf_ratio_IgG+rremove("ylab")
figure <- ggarrange(
  A,B,labels = c( "A","B"),nrow = 2,
  common.legend = TRUE, legend = "none")

annotate_figure(figure, 
                left = text_grob(
                  "Maternal to Fetal transfer ratio (Log10 μg/ml)", 
                  rot = 90, vjust = 1,color="darkblue",size = 17,
                  face = "bold",hjust = 0.45)
                )
```

